### 2021-03-28 newvariant.tex
adding one more line in discussion

Here, we explored how the generation-interval distribution shapes the link between relative strength and speed of the new variant.
We define relative strength as the ratio between reproduction numbers ($\rho=\Ry{var}/\Ry{wt}$) and relative speed as the difference between growth rates ($\delta=\ry{var}-\ry{wt}$) of the variant and the wild type.
When the generation-interval distributions are assumed to be identical, we find that estimates of $\hat{\rho}$ decreases with $r_w$ whereas $\hat{\delta}$ increase with $\RR_w$.
When we account for possible differences in generation-interval distributions, these relationships can change directions and further lead to biases in these estimates.
We also show that differences in generation intervals lead to different conclusions about the effectiveness of interventions:
if the variant has longer or shorter generation intervals than the wild type, we should prioritize speed- or strength-like interventions, respectively.

>>>>

Here, we explored how the generation-interval distribution shapes the link between relative strength and speed of the new variant.
We define relative strength as the ratio between reproduction numbers ($\rho=\Ry{var}/\Ry{wt}$) and relative speed as the difference between growth rates ($\delta=\ry{var}-\ry{wt}$) of the variant and the wild type.
When the generation-interval distributions are assumed to be identical, we find that estimates of $\hat{\rho}$ decreases with $r_w$ whereas $\hat{\delta}$ increase with $\RR_w$.
When we account for possible differences in generation-interval distributions, these relationships can change directions and further lead to biases in these estimates.
We show how these biases might be assessed in practice.
We also discuss that differences in generation intervals lead to different conclusions about the effectiveness of interventions:
if the variant has longer or shorter generation intervals than the wild type, we should prioritize speed- or strength-like interventions, respectively.
